---
title: "Pixture"
date: "`r format(Sys.time(), '%d-%b-%Y')`"
output:
  html_document:
    theme: flatly
    self_contained: false
    number_sections: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Usage

This is a demo of the **pixture** image gallery. The only mandatory input required is one or more paths/URLs to image(s).

```{r}
library(pixture)
paths <- c("https://images.pexels.com/photos/572897/pexels-photo-572897.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/7604425/pexels-photo-7604425.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/4666748/pexels-photo-4666748.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/4932184/pexels-photo-4932184.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/4210900/pexels-photo-4210900.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/3126574/pexels-photo-3126574.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/167699/pexels-photo-167699.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/1376201/pexels-photo-1376201.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/7919/pexels-photo.jpg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/2437291/pexels-photo-2437291.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/1679772/pexels-photo-1679772.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/1183099/pexels-photo-1183099.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/1813513/pexels-photo-1813513.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/931018/pexels-photo-931018.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/267074/pexels-photo-267074.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
           "https://images.pexels.com/photos/4622893/pexels-photo-4622893.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940")
```

Clicking on the thumbnail opens up the full image in a lightbox.

```{r}
pixture::pixture(paths[1])
```

The whole gallery can be browsed through the lightbox using left or right arrow keys.

```{r}
pixture(paths[1:2])
```

```{r}
pixture(paths)
```

# Captions

Optionally, captions can be added to the images which are visible when viewed in the lightbox.

```{r}
pixture(paths,caption=c("night", "forest", "shark", "coconut trees", "flowers", "field", "misty", "leaves", "sunset", "mountains", "swamp", "rainstorm", "leaves", "beach", "leopard", "sunflower"))
```

Images without captions can be set as NA.

```{r}
pixture(paths[1:4], caption=c("night", "forest", NA, "coconut trees"))
```

# Dimensions

The arguments `h` and `w` is used to adjust the height and width of images in the grid. This value is a string in any valid css unit.

```{r}
pixture::pixture(paths, w="50px")
```

```{r}
pixture::pixture(paths, h="3em", w="3em")
```

# Gap

The argument `gap` is used to control spacing between images in the grid. This value is a string in any valid css unit.

```{r}
pixture::pixture(paths[1:4], gap="20px")
```

```{r}
pixture::pixture(paths, gap="0", w="45px")
```

# Local images

Local images can be provided as relative or absolute paths. Here is an example. Note that this only works locally.

```{r,eval=FALSE}
paths <- list.files(system.file("extdata/images", package="pixture"), full=TRUE)
pixture::pixture(paths)
```

For your own local images, replace `system.file("extdata/images", package="pixture")` with a path like `images/` relative to the Rmd file.

# Shiny

This is an example of a shiny app using pixture.

```{r,eval=FALSE}
# pixture shiny app

library(shiny)
library(pixture)

ids <- c("572897",
          "7604425",
          "4666748",
          "4932184",
          "4210900",
          "3126574",
          "167699",
          "1376201",
          "2437291",
          "1679772",
          "1183099",
          "1813513",
          "931018",
          "267074",
          "4622893")

caption <- c("night;forest;shark;coconut trees;flowers;field;misty;leaves;mountains;swamp;rainstorm;leaves;beach;leopard;sunflower")

ui <- fluidPage(
    titlePanel("Pixture Demo"),
    sidebarLayout(
        sidebarPanel(width=3,
            selectInput("ids", "Image IDs", choices=ids, selected=ids, multiple=TRUE),
            checkboxInput("caption_check", "Use captions", value=FALSE),
            uiOutput("caption_ui"),
            textInput("h", label = "Image height", value="200px"),
            textInput("w", label = "Image width", value="200px"),
            textInput("gap", label = "Grid gap", value="6px"),
            HTML("Images from <a href='https://www.pexels.com/'>Pexels.</a>")
        ),
        mainPanel(width=9,
            pixture::pixtureOutput("pixture")
        )
    )
)

server <- function(input, output) {
    output$caption_ui <- renderUI({
        if(input$caption_check) {
            textInput("caption", "Caption", value=caption)
        }
    })

    output$pixture <- pixture::renderPixture({
        paths <- paste0("https://images.pexels.com/photos/", input$ids, "/pexels-photo-", input$ids, ".jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940")

        if(input$caption_check){
          if(!is.null(input$caption)){
            cpt <- unlist(strsplit(input$caption, ";"))
            if(length(cpt)!=length(paths)) stop("Number of captions do not match number of images.")
            pixture::pixture(paths, caption=cpt, h = input$h, w = input$w, gap = input$gap)
          }
        }else{
            pixture::pixture(paths, h = input$h, w = input$w, gap = input$gap)
        }


    })
}

shinyApp(ui = ui, server = server)
```

To try out a demo app, run `pixture::runPixture()`.

To use local images in Shiny, the images can be added to the `www` directory and the paths are relative. For example; an image at `app/www/images/image.jpg` is referenced in the app as `images/image.jpg`.

