---
title: "Lightbox usage"
subtitle: "Customize the lightbox"
date: last-modified
date-format: "DD-MMM-YYYY"
format:
  html:
    toc: true
    number-sections: true
    code-overflow: wrap
    resources:
      - images
---

This is a demo on customizing the lightbox. **pixture** uses [GLightbox](https://biati-digital.github.io/glightbox/) for lightbox functionality. You can pass options to the lightbox using the `lightbox` parameter as a list. The available options for glightbox can be found at [here](https://github.com/biati-digital/glightbox?tab=readme-ov-file#lightbox-options).

```{r}
#| code-fold: true

library(pixture)
paths <- c(
  "https://images.pexels.com/photos/572897/pexels-photo-572897.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/7604425/pexels-photo-7604425.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/4666748/pexels-photo-4666748.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/4932184/pexels-photo-4932184.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/4210900/pexels-photo-4210900.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/3126574/pexels-photo-3126574.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/167699/pexels-photo-167699.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/1376201/pexels-photo-1376201.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/7919/pexels-photo.jpg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/2437291/pexels-photo-2437291.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/1679772/pexels-photo-1679772.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/1183099/pexels-photo-1183099.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/1813513/pexels-photo-1813513.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/931018/pexels-photo-931018.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/267074/pexels-photo-267074.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940",
  "https://images.pexels.com/photos/4622893/pexels-photo-4622893.jpeg?auto=compress&cs=tinysrgb&dpr=2&h=650&w=940"
)
captions <- c(
  "A beautiful night sky filled with stars.",
  "A dense forest with tall trees.",
  "A shark swimming in the ocean.",
  "Coconut trees swaying in the breeze.",
  "A vibrant field of flowers in bloom.",
  "A vast field under a clear sky.",
  "A misty morning in the mountains.",
  "Close-up of green leaves on a tree.",
  "A stunning sunset over the horizon.",
  "Majestic mountains behind an idyllic landscape.",
  "A swamp with lush vegetation.",
  "A rainstorm with dark clouds and lightning.",
  "Raindrops on lush green tropical leaves.",
  "A sandy beach with crystal clear water.",
  "A leopard in snowy weather conditions.",
  "A close-up of a bright sunflower."
)
```

Clicking on the image opens up the full image in a lightbox. The whole gallery can be browsed through in the lightbox using left or right arrow keys.

```{r}
pixfigure(paths[1:2], caption = captions[1:2])
pixgallery(paths[1:6], caption = captions[1:6])
pixcarousel(paths[1:6], caption = captions[1:6])
```

**glightbox** options can be passed as a list to the `lightbox` parameter. Below are some examples of customizing the lightbox.

Enable looping of images in the lightbox using `loop = TRUE`. Zooming can be disabled using `zoomable = FALSE`.

```{r}
pixfigure(
  paths[1:2],
  caption = captions[1:2],
  lightbox = list(loop = TRUE, zoomable = FALSE)
)
pixgallery(
  paths[1:6],
  caption = captions[1:6],
  lightbox = list(loop = TRUE, zoomable = FALSE)
)
pixcarousel(
  paths[1:6],
  caption = captions[1:6],
  lightbox = list(loop = TRUE, zoomable = FALSE)
)
```

## Session

```{r}
sessionInfo()
```
